quollr: An R Package for Visualizing 2D Models from Nonlinear Dimension Reductions in High Dimensional Space

### 2024-06-04 paper-quollr.Rmd
Added plan for the application

<!-- hoe the data are generated and from which package I got the data-->

@@

nldr_prism <- tsne_prism_scaled |> 
  ggplot(aes(x = tSNE1, y = tSNE2)) + 
  geom_point(alpha=0.5, colour="#000000", size = 0.5)

nldr_prism
```

## Selecting parameter values for the model

>>>>

<!-- how the data are generated and from which package I got the data-->

@@

nldr_prism1 <- tsne_prism_scaled |> 
  ggplot(aes(x = tSNE1, y = tSNE2)) + 
  geom_point(alpha=0.5, colour="#000000", size = 0.5)

nldr_prism1
```

## Deciding an appropriate fit

<!--select based on looking at b_non_empty vs log(MSE)-->
<!--select a choice for b_non_empty-->

## Fit the appropriate model

### Selecting parameter values for the model

#### Choice of bins

#### Removal of low-density bins

#### Removing long edges
